---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

Data analysis for the All Coral Experiment #2021. Physiological variables:  
AFDW
Flow Cytometry (cell counts)
Protien
Biomass
BW
PAM


#Data and libraries
```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library('ggpubr')
library(lmerTest)
library(car)
library(emmeans)
library(gridExtra)
library(multcomp)
library(reshape)

```

Load meta
```{r}
meta  <- read.csv("Data/Master_Metadata_20190402.csv")
#remove frags that re duplicated or T3
meta<-meta[!(meta$X=="REMOVE"),]

# load in datasheets 
#Ashfreedryweight, Wax dipping, Total airbrush volume, metadata

AFDW <- read.csv("Data/AFDW_TT17_20190409.csv")

WaxDipping <- read.csv("Data/WaxDipping_Results_20190403.csv")

Slurry <- read.csv("Data/TT17_airbrush_totalVol_20190420.csv")


```


#AFDW
```{r} 

SA<-WaxDipping
SA<- SA[,c("Frag.ID","Surface.area")] # keep only columns you need

# merge AFDW and slurry
AFDW.slurry <- merge(AFDW, Slurry)
AFDW.slurry$AFDW.mg.ml <- AFDW.slurry$AFDW.g.mL*1000  # grams to mg
AFDW.slurry$AFDWmg <-AFDW.slurry$AFDW.mg.ml*AFDW.slurry$TotalVolume # now we have mg of AFDW

# SA cm2 and AFDW g/mL --> mg/cm2

# merge
biomass <- merge(AFDW.slurry, SA)
biomass$Surface.area<-as.numeric(as.character(biomass$Surface.area))
biomass<- biomass[,c("Frag.ID", "AFDWmg", "Surface.area")] # keep only columns you need
biomass$AFDWmg.cm2 <-biomass$AFDWmg/biomass$Surface.area # mg/cm2

# merge with metadata to plot by treatments
biomass2 <- merge(biomass, meta)


# Mcap_biomass
biomass2_mean <- ddply(biomass2, c("Treatment", "Species", "Time.Point"), summarise, #summarize cell counts
                 N    = length(AFDWmg.cm2[!is.na(AFDWmg.cm2)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                 mean = mean(AFDWmg.cm2, na.rm=TRUE), #calculate mean of response variable, removing NA's
                 sd   = sd(AFDWmg.cm2, na.rm=TRUE), #calculate standard deviation
                 se   = sd / sqrt(N), #calculate standard error
                 max = max(AFDWmg.cm2, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
biomass2_mean #display table
#Mcap_biomass_mean <-Mcap_biomass_mean[-3,] # Remove T0
#biomass2_mean

# Make "BOTH" into Ambeint and High...THIS IS UGLY CODE BUT IT WORKS
# Mcap 
#Mcap_biomass_mean<-subset(biomass2_mean, Species=="Montipora_capitata") #Subset Mcap

#Mcap_biomass_mean_Both<-Mcap_biomass_mean #copy df
#row.names.remove <- c("1","2","13","14") #remove high and amb by row numbers
#Mcap_biomass_mean_Both<-Mcap_biomass_mean_Both[!(row.names(Mcap_biomass_mean_Both) %in% row.names.remove), ] #remove

#Mcap_biomass_mean_Both2<-Mcap_biomass_mean_Both # make a copy of the BOTH df
#Mcap_biomass_mean_Both[Mcap_biomass_mean_Both=="Both"]<-"Ambient"  #rename "Both" to "Ambient"
#Mcap_biomass_mean_Both2[Mcap_biomass_mean_Both2=="Both"]<-"High"  #rename "Both" to "High"

#row.names.remove <- c("9") #remove "high and amb by row numbers "both""
#Mcap_biomass_mean<-Mcap_biomass_mean[!(row.names(Mcap_biomass_mean) %in% row.names.remove), ]
#Mcap_biomass_mean<-rbind(Mcap_biomass_mean,Mcap_biomass_mean_Both,Mcap_biomass_mean_Both2) #bind together

#Mcap 
Mcap_biomass_mean<-subset(biomass2_mean, Species=="Montipora_capitata") #Subset Mcap
# Pcomp 
Pcomp_biomass_mean<-subset(biomass2_mean, Species=="Porites_compressa") #Subset Pcomp
# Pacu 
Pacu_biomass_mean<-subset(biomass2_mean, Species=="Pocillopora_acuta") #Subset Pacu
# Pvar 
Pvar_biomass_mean<-subset(biomass2_mean, Species=="Pavona_varians") #Subset Pvar



#Stats - T0 is n=6, not n=12

Biomass_stats<-biomass2

hist(Biomass_stats$AFDWmg.cm2) 
Biomass_stats$AFDWmg.cm2_log<-log10(Biomass_stats$AFDWmg.cm2+1)
hist(Biomass_stats$AFDWmg.cm2_log) #normal (use)

Biomass_model<-lmer(AFDWmg.cm2_log~Time.Point*Treatment*Species+(1|Parent.ID)+(1|Tank.num), Biomass_stats)
anova(Biomass_model) 
qqPlot(residuals(Biomass_model)) 

  emm<-emmeans(Biomass_model,  ~ Time.Point*Treatment|Species, adjust="Tukey")
cld(emm)
pairs(emm)

```
###PLOTS
```{r}
#plot Mcap
Mcap_biomass_plot<-ggplot(data=Mcap_biomass_mean, aes(x=Time.Point, y=mean, group = Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = F)+
  geom_point(aes(color=Treatment), size=4, show.legend = F)+
  geom_line(aes(color=Treatment), linetype=2, show.legend = F)+
  scale_color_manual(values=c("dodgerblue3", "darkred"))+
  xlab("") + #Label the X Axis
  ylim(0, 10) + #set Y limits
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("Tissue biomass mg cm"^"-2"))) +
  ggtitle("Montipora capitata")+
  theme(plot.title = element_text(size=20, face = "italic"));Mcap_biomass_plot

# Pcomp 

Pcomp_biomass_plot<-ggplot(data=Pcomp_biomass_mean, aes(x=Time.Point, y=mean, group = Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = F)+
  geom_point(aes(color=Treatment), size=4, show.legend = F)+
  geom_line(aes(color=Treatment), linetype=2, show.legend = F)+
  scale_color_manual(values=c("dodgerblue3", "darkred"))+
  xlab("") + #Label the X Axis
  ylab("") + #Label the X Axis
  ylim(0, 10) + #set Y limits
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  #ylab(expression(paste("Tissue biomass mg cm"^"-2"))) +
  ggtitle("Porites compressa")+
  theme(plot.title = element_text(size=20, face = "italic"));Pcomp_biomass_plot

# Pvar 

Pvar_biomass_mean_plot<-ggplot(data=Pvar_biomass_mean, aes(x=Time.Point, y=mean, group = Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = F)+
  geom_point(aes(color=Treatment), size=4, show.legend = F)+
  geom_line(aes(color=Treatment), linetype=2, show.legend = F)+
  scale_color_manual(values=c("dodgerblue3", "darkred"))+
  xlab("") + #Label the X Axis
  ylim(2.5, 6) + #set Y limits
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("Tissue biomass mg cm"^"-2"))) +
  ggtitle("Pavona varians")+
  theme(plot.title = element_text(size=20, face = "italic"));Pvar_biomass_mean_plot

# Pacu 

Pacu_biomass_mean_plot<-ggplot(data=Pacu_biomass_mean, aes(x=Time.Point, y=mean, group = Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = F)+
  geom_point(aes(color=Treatment), size=4, show.legend = F)+
  geom_line(aes(color=Treatment), linetype=2, show.legend = F)+
  scale_color_manual(values=c("dodgerblue3", "darkred"))+
  xlab("") + #Label the X Axis
  ylab("") + #Label the Y Axis
  ylim(0, 10) + #set Y limits
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        plot.background =element_blank(), #Set the plot background
        text = element_text(size=18),  # set element text
        legend.key = element_blank()) + #Set plot legend key
  #ylab(expression(paste("Tissue biomass mg cm"^"-2"))) +
  ggtitle("Pocillopora acuta")+
  theme(plot.title = element_text(size=20,face = "italic"));Pacu_biomass_mean_plot


###### All plots together
Mcap_biomass_plot_plot<-Mcap_biomass_plot+ theme(legend.position = "none") #remove legend
Pcomp_biomass_plot<-Pcomp_biomass_plot+ theme(legend.position = "none") #remove legend
Pvar_biomass_mean_plot<-Pvar_biomass_mean_plot+ theme(legend.position = "none") #remove legend
Pacu_biomass_mean_plot<-Pacu_biomass_mean_plot+ theme(legend.position = "none") #remove legend

grid.arrange(Mcap_FC_Plot, Pcomp_FC_Plot, Pvar_FC_Plot,Pacu_FC_Plot, nrow = 2)

```

# Flow cytometry  cell counts
```{r}
#import data
Std.curve <- read.csv("Data/standard_curve_fcm20181312.csv")

###notes: 2289 isn't anywhere. 

PlateA <- read.csv("Data/Symbio.Counts.Dec.14.2018.PlateA.csv")
PlateA <- subset(PlateA, Gate.Name == "Symbiodinium")       # keep only Symbiodinium rows
keepA <- c("Sample.Name", "Concentration") # keep only Sample.name and concentration
PlateA <- PlateA[keepA]
A_meta <- read.csv("Data/TT17_FC_PlateA.csv") # load Plate A location data
PlateA <- merge(PlateA, A_meta)   # merge with location data
PlateA <-merge(PlateA, meta, all.x = TRUE) # merge with Sample metadata
PlateA <- na.omit(PlateA) # omit NAs

PlateB <- read.csv("Data/Symbio.Counts.Dec.14.2018.PlateB1.csv")
PlateB$Concentration<-as.numeric(as.character(PlateB$Concentration)) # this is loading in as a factor, not sure why
PlateB <- subset(PlateB, Gate.Name == "Symbiodinium")
keepB <- c("Sample.Name", "Concentration")
PlateB <- PlateB[keepB]
B_meta <- read.csv("Data/TT17_FC_PlateB.csv") # lood Plate B location data
PlateB <- merge(PlateB, B_meta)
PlateB <-merge(PlateB, meta, all.x = TRUE)
PlateB <- na.omit(PlateB)

PlateC <- read.csv("Data/Symbio.Counts.Dec.14.2018.PlateCredo.csv")
PlateC$Concentration<-as.numeric(as.character(PlateC$Concentration)) # this is loading in as a factor, not sure why
PlateC <- subset(PlateC, Gate.Name == "Symbiodinium")
keepC <- c("Sample.Name", "Concentration")
PlateC <- PlateC[keepC]
C_meta <- read.csv("Data/TT17_FC_PlateCredo.csv") # lood Plate C location data
PlateC <- merge(PlateC, C_meta)
PlateC <-merge(PlateC, meta, all.x = TRUE)
PlateC <- na.omit(PlateC)
#note: Frag.ID 403 Pacu seems abnormally high

PlateE <- read.csv("Data/Symbio.Count.apr.02.2019.PlateE.csv")
PlateE$Concentration<-as.numeric(as.character(PlateE$Concentration)) # this is loading in as a factor, not sure why
PlateE <- subset(PlateE, Gate.Name == "Symbiodinium")
keepE <- c("Sample.Name", "Concentration")
PlateE <- PlateE[keepE]
E_meta <- read.csv("Data/TT17_FC_PlateE.csv") # lood Plate A location data
PlateE <- merge(PlateE, E_meta)
PlateE <-merge(PlateE, meta, all.x = TRUE)
PlateE <- na.omit(PlateE)


# Bind all runs together
tData <- rbind(PlateA, PlateB, PlateC, PlateE)
tData$Parent.ID<- as.factor(tData$Parent.ID) #for some reason, "Concentration" was a chr not numeric. Check by calling str()

# Create column to relate to standard curve
tData$corrected <- tData$Concentration*3.2959 # <- also confirm you did this correctly. 

# Use Slurry
#merge with tdata
tData <- merge(tData, Slurry)
tData$TotalVolume <- tData$TotalVolume * 1000 # change total volume to from mL to uL

#use SA for slurry

#merge with tData, make numeric
tData <- merge(tData, SA)
tData$Surface.area<- as.numeric(as.character(tData$Surface.area))

#Subset by Species and correct for 10% dilutions in Mcap and Pcomp
Mcap_FC <- subset(tData, Species == "Montipora_capitata")
Mcap_FC$corrected <- Mcap_FC$corrected*10 # to compensate for the 10% dultion

Pcomp_FC <- subset(tData, Species == "Porites_compressa")
Pcomp_FC$corrected <- Pcomp_FC$corrected*10 # to compensate for the 10% dultion

Pvar_FC <- subset(tData, Species == "Pavona_varians") #not diluted
Pacu_FC <- subset(tData, Species == "Pocillopora_acuta") #not diluted

# Create new column for total cells in total slurry
Mcap_FC$Tot.zoox <- Mcap_FC$corrected*(Mcap_FC$TotalVolume)
Pcomp_FC$Tot.zoox <- Pcomp_FC$corrected*(Pcomp_FC$TotalVolume)
Pvar_FC$Tot.zoox <- Pvar_FC$corrected*(Pvar_FC$TotalVolume)
Pacu_FC$Tot.zoox <- Pacu_FC$corrected*(Pacu_FC$TotalVolume)

# Calculate zoox/cm2
Mcap_FC$zoox.cm2<-Mcap_FC$Tot.zoox/Mcap_FC$Surface.area
Pcomp_FC$zoox.cm2<-Pcomp_FC$Tot.zoox/Pcomp_FC$Surface.area
Pvar_FC$zoox.cm2<-Pvar_FC$Tot.zoox/Pvar_FC$Surface.area
Pacu_FC$zoox.cm2<-Pacu_FC$Tot.zoox/Pacu_FC$Surface.area

FC_Data <- rbind(Mcap_FC, Pcomp_FC, Pvar_FC, Pacu_FC) #combine

#Stats


hist(FC_Data$zoox.cm2) 
FC_Data$zoox.cm2_log<-log10(FC_Data$zoox.cm2+1)
hist(FC_Data$zoox.cm2_log) #normal (use)

CellCount_model<-lmer(zoox.cm2_log~Time.Point*Treatment*Species+(1|Parent.ID)+(1|Tank.num), FC_Data)
anova(CellCount_model) 
qqPlot(residuals(CellCount_model)) 

  emm<-emmeans(CellCount_model,  ~ Time.Point*Treatment|Species, adjust="Tukey")
cld(emm)
pairs(emm)













#mean tables
# Mcap
Mcap_FC_Sum <- ddply(Mcap_FC, c("Treatment", "Species", "Time.Point"), summarise, #summarize cell counts
                   N    = length(zoox.cm2[!is.na(zoox.cm2)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                   mean = mean(zoox.cm2, na.rm=TRUE), #calculate mean of response variable, removing NA's
                   sd   = sd(zoox.cm2, na.rm=TRUE), #calculate standard deviation
                   se   = sd / sqrt(N), #calculate standard error
                   max = max(zoox.cm2, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
Mcap_FC_Sum #display table

# Pcomp
Pcomp_FC_Sum <- ddply(Pcomp_FC, c("Treatment", "Species", "Time.Point"), summarise, #summarize cell counts
                   N    = length(zoox.cm2[!is.na(zoox.cm2)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                   mean = mean(zoox.cm2, na.rm=TRUE), #calculate mean of response variable, removing NA's
                   sd   = sd(zoox.cm2, na.rm=TRUE), #calculate standard deviation
                   se   = sd / sqrt(N), #calculate standard error
                   max = max(zoox.cm2, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
Pcomp_FC_Sum #display table


# Pvar
Pvar_FC_Sum <- ddply(Pvar_FC, c("Treatment", "Species", "Time.Point"), summarise, #summarize cell counts
                   N    = length(zoox.cm2[!is.na(zoox.cm2)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                   mean = mean(zoox.cm2, na.rm=TRUE), #calculate mean of response variable, removing NA's
                   sd   = sd(zoox.cm2, na.rm=TRUE), #calculate standard deviation
                   se   = sd / sqrt(N), #calculate standard error
                   max = max(zoox.cm2, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
Pvar_FC_Sum #display table

# Pacu
Pacu_FC_Sum <- ddply(Pacu_FC, c("Treatment", "Species", "Time.Point"), summarise, #summarize cell counts
                   N    = length(zoox.cm2[!is.na(zoox.cm2)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                   mean = mean(zoox.cm2, na.rm=TRUE), #calculate mean of response variable, removing NA's
                   sd   = sd(zoox.cm2, na.rm=TRUE), #calculate standard deviation
                   se   = sd / sqrt(N), #calculate standard error
                   max = max(zoox.cm2, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
Pacu_FC_Sum #display table

```

#Line plots
```{r}
# Mcap 

Mcap_FC_lineplot<-ggplot(data=Mcap_FC_Sum, aes(x=Time.Point, y=mean, group = Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Treatment), size=4, show.legend = T)+  
  geom_line(aes(color=Treatment),linetype="dotted")+
  scale_color_manual(values=c('blue','red'))+
   geom_point(shape = 1,size = 4,colour = "black")+
  xlab("Time Point") + #Label the X Axis
       scale_y_log10()+
      ylim(0, 4000000)+
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border 
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("cells"))) +
  ggtitle("Mcap Flow Cytometry")+
  theme(plot.title = element_text(size=20, face = "italic", hjust=0.5));Mcap_FC_lineplot

# Pcomp 

Pcomp_FC_lineplot<-ggplot(data=Pcomp_FC_Sum, aes(x=Time.Point, y=mean, group = Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Treatment), size=4, show.legend = T)+  
  geom_line(aes(color=Treatment),linetype="dotted")+
  scale_color_manual(values=c('blue','red'))+
   geom_point(shape = 1,size = 4,colour = "black")+
  xlab("Time Point") + #Label the X Axis
       scale_y_log10()+
    ylim(0, 4000000)+
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border 
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("cells"))) +
  ggtitle("Pcomp Flow Cytometry")+
  theme(plot.title = element_text(size=20, face = "italic", hjust=0.5));Pcomp_FC_lineplot


# Pvar 

Pvar_FC_lineplot<-ggplot(data=Pvar_FC_Sum, aes(x=Time.Point, y=mean, group = Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Treatment), size=4, show.legend = T)+  
  geom_line(aes(color=Treatment),linetype="dotted")+
  scale_color_manual(values=c('blue','red'))+
   geom_point(shape = 1,size = 4,colour = "black")+
  xlab("Time Point") + #Label the X Axis
       scale_y_log10()+
    ylim(0, 4000000)+
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border 
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("cells"))) +
  ggtitle("Pvar Flow Cytometry")+
  theme(plot.title = element_text(size=20, face = "italic", hjust=0.5));Pvar_FC_lineplot

# Pacu 

Pacu_FC_lineplot<-ggplot(data=Pacu_FC_Sum, aes(x=Time.Point, y=mean, group = Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Treatment), size=4, show.legend = T)+  
  geom_line(aes(color=Treatment),linetype="dotted")+
  scale_color_manual(values=c('blue','red'))+
   geom_point(shape = 1,size = 4,colour = "black")+
  xlab("Time Point") + #Label the X Axis
       scale_y_log10()+
  ylim(0, 4000000)+
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border 
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("cells"))) +
  ggtitle("Pacu Flow Cytometry")+
  theme(plot.title = element_text(size=20, face = "italic", hjust=0.5));Pacu_FC_lineplot

###### All plots together
Mcap_FC_lineplot<-Mcap_FC_lineplot+ theme(legend.position = "none") #remove legend
Pcomp_FC_lineplot<-Pcomp_FC_lineplot+ theme(legend.position = "none") #remove legend
Pvar_FC_lineplot<-Pvar_FC_lineplot+ theme(legend.position = "none") #remove legend
Pacu_FC_lineplot<-Pacu_FC_lineplot+ theme(legend.position = "none") #remove legend

grid.arrange(Mcap_FC_lineplot, Pcomp_FC_lineplot, Pvar_FC_lineplot,Pacu_FC_lineplot, nrow = 2)

```
#Buoyant Weight/Calcification

calibration (not sure what this does)
```{r}
BWCalData <- read.csv('Data/Bouyant_weight_calibration_curve.csv')
#Data with Standard weights in grams in deionized water, saltwater, and the temp that they were measured at

### Standard Cruve
#plot relationship between temp and Standard in fresh and salt water
plot(BWCalData$Temp, BWCalData$StandardSalt, col = 'red', ylab = 'Salt Weight (g)', xlab = 'Temp C')
par(new=TRUE)
plot(BWCalData$Temp, BWCalData$StandardFresh, col = 'blue',xaxt="n",yaxt="n",xlab="",ylab="")
axis(4)
mtext("'Fresh Weight (g)'",side=4,line=3)
legend("topleft",col=c("red","blue"),lty=1,legend=c("Salt","Fresh"), bty = "n")

#linear regression between temp and Standard
#Salt
StandardSaltModel <- lm(BWCalData$StandardSalt~BWCalData$Temp)
summary(StandardSaltModel)
summary(StandardSaltModel)$r.squared
StandardSaltModel$coef

#Fresh
StandardFreshModel <- lm(BWCalData$StandardFresh~BWCalData$Temp)
summary(StandardFreshModel)
summary(StandardFreshModel)$r.squared
StandardFreshModel$coef

```
Analysis 
```{r}

#load coral weight data
BW.data <-read.csv('Data/BW_TT17.csv') # this is a file I compiled with all dates

# merge to sample data for sorting
AllBWdata<-merge(BW.data, meta, by = "Frag.ID")

## Split data by species, change to numeric
Mcap_BW<- subset(AllBWdata, Species =="Montipora_capitata")
Mcap_BW$Temp.C <- as.numeric(as.character(Mcap_BW$Temp.C))
BW_Mcap <- Mcap_BW$Mass.g
Temp_Mcap <- Mcap_BW$Temp.C 

Pcomp_BW<- subset(AllBWdata, Species =="Porites_compressa")
Pcomp_BW$Temp.C <- as.numeric(as.character(Pcomp_BW$Temp.C))
BW_Pcomp <- Pcomp_BW$Mass.g
Temp_Pcomp <- Pcomp_BW$Temp.C 

Pvar_BW<- subset(AllBWdata, Species =="Pavona_varians")
Pvar_BW$Temp.C <- as.numeric(as.character(Pvar_BW$Temp.C))
BW_Pvar <- Pvar_BW$Mass.g
Temp_Pvar <- Pvar_BW$Temp.C 

Pacu_BW<- subset(AllBWdata, Species =="Pocillopora_acuta")
BW_Pacu <- Pacu_BW$Mass.g
Temp_Pacu <- Pacu_BW$Temp.C 
```
Montipora capitata
```{r}
BWCalc_Mcap <- function(StandardAir= 39.092, Temp, BW, CoralDensity = 2.03){
  #Parameters---------------------------------------------------------------
  # StandardAir is the weight of the Standard in air (Default set at 39.092 grams weighed on balance)
  # Temp is the temperature of the water during the coral measurement
  # BW is the buoywant weight of the coral
  # CoralDensity <- 2.03 #g cm-3, set aragonite density for Montipora from literature 
  #Montipora Arag = 2.03 g cm-3 average from table 2 in Anthony 2003 Functional Ecology 17:246-259
  # Porites asteroides T Hughes 1987 1.69 at 5m (KB got 1.82)
  # below: Medellin-Maldonado et al 2016
  # Pavona varians 1.04 +-0.07
  # panama 8.5380° N, 80.7821° W, 
  # coasta rica 9.7489° N, 83.7534° W
  # mexico la entrega 15.7424° N, 96.1282° W
  # hawaii 19.8968° N, 155.5828° W
  # Pocillopora 1.78 +- 0.31
  
  
  # You can change the density to literatrue values for the specific coral species of interest in the function. 
  
  #Calculation------------------------------------------------------------
  #Step 1: correct the Standard weights for temperature
  # StandardFresh is the weight of the Standard in  fresh water at temp x
  # StandardSalt is the weight of the Standard in salt water at temp x
  
  # This is based on a calibration curve for Standards weighed in fresh and salt water at many temps
StandardFresh <- StandardFreshModel$coef[-1]*Temp + StandardFreshModel$coef[1] 
StandardSalt <- StandardSaltModel$coef[-1]*Temp + StandardSaltModel$coef[1] 
  
  # Step 2: Use weight in air and freshwater of the glass Standard to calculate
  # the density of the Standard (Davies eq. 4)
FreshDensity <- 1 #Fresh water has a density of 1 g/cm3
StandardDensity <- FreshDensity/(1-(StandardFresh/StandardAir)) 
  
  # Step 3: Calculate the density of seawater using the density of the Standard
  # (Spencer Davies eq. 3)
SWDensity <- StandardDensity*(1-(StandardSalt/StandardAir))
  
  # Step 4: Calculate the dry weight of the coral (Davies eq. 1)
CoralWeight <- BW_Mcap/(1-(SWDensity/CoralDensity))
  
  return(CoralWeight) #returns coral dry weights in g
}
  
Mcap_BW$Dry.Weigh.g <- BWCalc_Mcap(BW=BW_Mcap, Temp=Temp_Mcap) #use function to calculate dry weight
hist(Mcap_BW$Dry.Weigh.g) #not normal
Mcap_BW$Dry.Weigh.g_log<-log10(Mcap_BW$Dry.Weigh.g+1)
hist(Mcap_BW$Dry.Weigh.g_log) #better still tail
boxplot(Mcap_BW$Dry.Weigh.g) #examine data
Mcap_BW <- Mcap_BW[!(Mcap_BW$Frag.ID == "797"),] # remove sample 797, error in BW record (impossible value)

# below, we are getting rid of columns we don't need anymore, and reorganizing the data by Fragment and clade/color and treatment. This way our time points wil be in the same row)
data_McapBW <- reshape(Mcap_BW, timevar = "TimePoint", drop = c("Mass.g","Temp.C", "Date","Tank", "X",  "Parent.ID", "Species","Time.Point", "Tank.num"), idvar=c("Frag.ID", "Treatment"), direction="wide")

# This calculates the growth rate, if you look it takes Timepoint1 subtracts timepoint0 and divides by timepoint 0, times 100
data_McapBW$time1.growth <- (((data_McapBW$Dry.Weigh.g.Time1 - data_McapBW$Dry.Weigh.g.Time0)/data_McapBW$Dry.Weigh.g.Time0)*100)/data_McapBW$Days.Time1 #calculate growth rate for time1
data_McapBW$time2.growth <- (((data_McapBW$Dry.Weigh.g.Time2 - data_McapBW$Dry.Weigh.g.Time1)/data_McapBW$Dry.Weigh.g.Time1)*100)/data_McapBW$Days.Time2 #calculate growth rate for time2

# mean, standard dev, and sem
time1_McapBW <-ddply(data_McapBW, .( Treatment), summarize, #For each subset of a data frame, apply function then combine results into a data frame.
              N=length(na.omit(time1.growth)), # the sample size of the light column summarized by Tank number
              mean = (mean(time1.growth, na.rm=TRUE)) ,  #take the average of the light column summarized by Tank number
              sd = sd(time1.growth, na.rm=TRUE) ,# the standard deviation of the temp column summarized by Tank number
              sem = (sd(time1.growth,na.rm=T)/sqrt(N))) #calculate the SEM as the sd/sqrt of the count or data length
time1_McapBW$Time <- "Time1"  # this puts these data in our "time1" dataframe

time2_McapBW <-ddply(data_McapBW, .( Treatment), summarize, #For each subset of a data frame, apply function then combine results into a data frame.
              N=length(na.omit(time2.growth)), # the sample size of the light column summarized by Tank number
              mean = (mean(time2.growth, na.rm=TRUE)) ,  #take the average of the light column summarized by Tank number
              sd = sd(time2.growth, na.rm=TRUE) ,# the standard deviation of the temp column summarized by Tank number
              sem = (sd(time2.growth,na.rm=T)/sqrt(N))) #calculate the SEM as the sd/sqrt of the count or data length
time2_McapBW$Time <- "Time2"  # this puts these data in our "time1" dataframe

#save this dataframe as "G"
G_McapA <- rbind(time1_McapBW[1,],time2_McapBW[1,])# Greate a new column that we rename each row by treatment
G_McapH <- rbind(time1_McapBW[2,],time2_McapBW[2,])# Greate a new column that we rename each row by treatment
G_Mcap<-rbind(G_McapA, G_McapH)
# Stress.Recovery column 
 # make new column that renames "time" to Stress or Recovery
G_Mcap$newtime = ifelse(G_Mcap$Time == "Time1", "Post-Stress", "Post-Recovery")
G_Mcap <- within(G_Mcap, newtime <- factor(newtime, levels = c("Post-Stress", "Post-Recovery"))) # Set order of levels so plots in right order



Mcap_BW_plot<-ggplot(data=G_Mcap, aes(x=newtime, y=mean, group = Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Treatment), size=4, show.legend = T)+  
  geom_line(aes(color=Treatment),linetype="dotted")+
  scale_color_manual(values=c("dodgerblue3", "darkred"))+
   geom_point(shape = 1,size = 4,colour = "black")+
  xlab("Time Point") + #Label the X Axis
      ylim(0, .7)+
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border 
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("Dry.Weigh.g"))) +
  ggtitle("Calcification Mcap")+
  theme(plot.title = element_text(size=20, face = "italic", hjust=0.5));Mcap_BW_plot


```
Porites compressa
```{r}

################################     PORITES COMPRESSA
BWCalc_Pcomp <- function(StandardAir= 39.092, Temp, BW, CoralDensity = 1.82){
  #Parameters---------------------------------------------------------------
  # StandardAir is the weight of the Standard in air (Default set at 39.092 grams weighed on balance)
  # Temp is the temperature of the water during the coral measurement
  # BW is the buoywant weight of the coral
  # CoralDensity <- 2.03 #g cm-3, set aragonite density for Montipora from literature 
  # Montipora Arag = 2.03 g cm-3 average from table 2 in Anthony 2003 Functional Ecology 17:246-259
  
  # Porites asteroides (T Hughes 1987 1.69 at 5m) (KB got 1.82)
  
  # below: Medellin-Maldonado et al 2016
  # Pavona varians 1.04 +-0.07
  # panama 8.5380° N, 80.7821° W, 
  # coasta rica 9.7489° N, 83.7534° W
  # mexico la entrega 15.7424° N, 96.1282° W
  # hawaii 19.8968° N, 155.5828° W
  # Pocillopora 1.78 +- 0.31
  
  
  # You can change the density to literatrue values for the specific coral species of interest in the function. 
  
  #Calculation------------------------------------------------------------
  #Step 1: correct the Standard weights for temperature
  # StandardFresh is the weight of the Standard in  fresh water at temp x
  # StandardSalt is the weight of the Standard in salt water at temp x
  
  # This is based on a calibration curve for Standards weighed in fresh and salt water at many temps
  StandardFresh <- StandardFreshModel$coef[-1]*Temp + StandardFreshModel$coef[1] 
  StandardSalt <- StandardSaltModel$coef[-1]*Temp + StandardSaltModel$coef[1] 
  
  # Step 2: Use weight in air and freshwater of the glass Standard to calculate
  # the density of the Standard (Davies eq. 4)
  FreshDensity <- 1 #Fresh water has a density of 1 g/cm3
  StandardDensity <- FreshDensity/(1-(StandardFresh/StandardAir)) 
  
  # Step 3: Calculate the density of seawater using the density of the Standard
  # (Spencer Davies eq. 3)
  SWDensity <- StandardDensity*(1-(StandardSalt/StandardAir))
  
  # Step 4: Calculate the dry weight of the coral (Davies eq. 1)
  CoralWeight <- BW_Pcomp/(1-(SWDensity/CoralDensity))
  
  return(CoralWeight) #returns coral dry weights in g
}


Pcomp_BW$Dry.Weigh.g <- BWCalc_Pcomp(BW=BW_Pcomp, Temp=Temp_Pcomp) #use function to calculate dry weight
hist(Pcomp_BW$Dry.Weigh.g) 
Pcomp_BW$Dry.Weigh.g_log<-log10(Pcomp_BW$Dry.Weigh.g+1)
hist(Pcomp_BW$Dry.Weigh.g_log) # normal
boxplot(Pcomp_BW$Dry.Weigh.g_log) #examine data

# below, we are getting rid of columns we don't need anymore, and reorganizing the data by Fragment and clade/color and treatment. This way our time points wil be in the same row)
data_PcompBW <- reshape(Pcomp_BW, timevar = "TimePoint", drop = c("Mass.g","Temp.C", "Date","Tank", "X", "Time.Point", "Parent.ID", "Species", "Tank.num"), idvar=c("Frag.ID", "Treatment"), direction="wide")

# This calculates the growth rate, if you look it takes Timepoint1 subtracts timepoint0 and divides by timepoint 0, times 100
data_PcompBW$time1.growth <- (((data_PcompBW$Dry.Weigh.g.Time1 - data_PcompBW$Dry.Weigh.g.Time0)/data_PcompBW$Dry.Weigh.g.Time0)*100)/data_PcompBW$Days.Time1 #calculate growth rate for time1
data_PcompBW$time2.growth <- (((data_PcompBW$Dry.Weigh.g.Time2 - data_PcompBW$Dry.Weigh.g.Time1)/data_PcompBW$Dry.Weigh.g.Time1)*100)/data_PcompBW$Days.Time2 #calculate growth rate for time2

# mean, standard dev, and sem
time1_PcompBW <-ddply(data_PcompBW, .( Treatment), summarize, #For each subset of a data frame, apply function then combine results into a data frame.
              N=length(na.omit(time1.growth)), # the sample size of the light column summarized by Tank number
              mean = (mean(time1.growth, na.rm=TRUE)) ,  #take the average of the light column summarized by Tank number
              sd = sd(time1.growth, na.rm=TRUE) ,# the standard deviation of the temp column summarized by Tank number
              sem = (sd(time1.growth,na.rm=T)/sqrt(N))) #calculate the SEM as the sd/sqrt of the count or data length
time1_PcompBW$Time <- "Time1"  # this puts these data in our "time1" dataframe

time2_PcompBW <-ddply(data_PcompBW, .( Treatment), summarize, #For each subset of a data frame, apply function then combine results into a data frame.
              N=length(na.omit(time2.growth)), # the sample size of the light column summarized by Tank number
              mean = (mean(time2.growth, na.rm=TRUE)) ,  #take the average of the light column summarized by Tank number
              sd = sd(time2.growth, na.rm=TRUE) ,# the standard deviation of the temp column summarized by Tank number
              sem = (sd(time2.growth,na.rm=T)/sqrt(N))) #calculate the SEM as the sd/sqrt of the count or data length
time2_PcompBW$Time <- "Time2"  # this puts these data in our "time1" dataframe

#save this dataframe as "G"
G_PcompA <- rbind(time1_PcompBW[1,],time2_PcompBW[1,])# Greate a new column that we rename each row by treatment
G_PcompH <- rbind(time1_PcompBW[2,],time2_PcompBW[2,])# Greate a new column that we rename each row by treatment
G_Pcomp<-rbind(G_PcompA, G_PcompH)
# Stress.Recovery column 
 # make new column that renames "time" to Stress or Recovery
G_Pcomp$newtime = ifelse(G_Pcomp$Time == "Time1", "Post-Stress", "Post-Recovery")
G_Pcomp <- within(G_Pcomp, newtime <- factor(newtime, levels = c("Post-Stress", "Post-Recovery"))) # Set order of levels so plots in right order



Pcomp_BW_plot<-ggplot(data=G_Pcomp, aes(x=newtime, y=mean, group = Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Treatment), size=4, show.legend = T)+  
  geom_line(aes(color=Treatment),linetype="dotted")+
  scale_color_manual(values=c("dodgerblue3", "darkred"))+
   geom_point(shape = 1,size = 4,colour = "black")+
  xlab("Time Point") + #Label the X Axis
      ylim(0, .7)+
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border 
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("Dry.Weigh.g"))) +
  ggtitle("Calcification Pcomp")+
  theme(plot.title = element_text(size=20, face = "italic", hjust=0.5));Pcomp_BW_plot

```
Pavona varians
```{r}
BWCalc_Pvar <- function(StandardAir= 39.092, Temp, BW, CoralDensity = 1.04){
  #Parameters---------------------------------------------------------------
  # StandardAir is the weight of the Standard in air (Default set at 39.092 grams weighed on balance)
  # Temp is the temperature of the water during the coral measurement
  # BW is the buoywant weight of the coral
  # CoralDensity <- 2.03 #g cm-3, set aragonite density for Montipora from literature 
  # Montipora Arag = 2.03 g cm-3 average from table 2 in Anthony 2003 Functional Ecology 17:246-259
  
  # Porites asteroides (T Hughes 1987 1.69 at 5m) (KB got 1.82)
  
  # below: Medellin-Maldonado et al 2016
  # Pavona varians 1.04 +-0.07
  # panama 8.5380° N, 80.7821° W, 
  # coasta rica 9.7489° N, 83.7534° W
  # mexico la entrega 15.7424° N, 96.1282° W
  # hawaii 19.8968° N, 155.5828° W
  # Pocillopora 1.78 +- 0.31
  
  
  # You can change the density to literatrue values for the specific coral species of interest in the function. 
  
  #Calculation------------------------------------------------------------
  #Step 1: correct the Standard weights for temperature
  # StandardFresh is the weight of the Standard in  fresh water at temp x
  # StandardSalt is the weight of the Standard in salt water at temp x
  
  # This is based on a calibration curve for Standards weighed in fresh and salt water at many temps
  StandardFresh <- StandardFreshModel$coef[-1]*Temp + StandardFreshModel$coef[1] 
  StandardSalt <- StandardSaltModel$coef[-1]*Temp + StandardSaltModel$coef[1] 
  
  # Step 2: Use weight in air and freshwater of the glass Standard to calculate
  # the density of the Standard (Davies eq. 4)
  FreshDensity <- 1 #Fresh water has a density of 1 g/cm3
  StandardDensity <- FreshDensity/(1-(StandardFresh/StandardAir)) 
  
  # Step 3: Calculate the density of seawater using the density of the Standard
  # (Spencer Davies eq. 3)
  SWDensity <- StandardDensity*(1-(StandardSalt/StandardAir))
  
  # Step 4: Calculate the dry weight of the coral (Davies eq. 1)
  CoralWeight <- BW_Pvar/(1-(SWDensity/CoralDensity))
  
  return(CoralWeight) #returns coral dry weights in g
}

Pvar_BW$Dry.Weigh.g <- BWCalc_Pvar(BW=BW_Pvar, Temp=Temp_Pvar) #use function to calculate dry weight
hist(Pvar_BW$Dry.Weigh.g) #not normal

boxplot(Pvar_BW$Dry.Weigh.g) #examine data
Pvar_BW$Dry.Weigh.g_log<-log10(Pvar_BW$Dry.Weigh.g+1)
hist(Pvar_BW$Dry.Weigh.g_log) #not normal


# below, we are getting rid of columns we don't need anymore, and reorganizing the data by Fragment and clade/color and treatment. This way our time points wil be in the same row)
data_PvarBW <- reshape(Pvar_BW, timevar = "TimePoint", drop = c("Mass.g","Temp.C", "Date","Tank", "X",  "Parent.ID", "Species","Time.Point", "Tank.num"), idvar=c("Frag.ID", "Treatment"), direction="wide")

# This calculates the growth rate, if you look it takes Timepoint1 subtracts timepoint0 and divides by timepoint 0, times 100
data_PvarBW$time1.growth <- (((data_PvarBW$Dry.Weigh.g.Time1 - data_PvarBW$Dry.Weigh.g.Time0)/data_PvarBW$Dry.Weigh.g.Time0)*100)/data_PvarBW$Days.Time1 #calculate growth rate for time1
data_PvarBW$time2.growth <- (((data_PvarBW$Dry.Weigh.g.Time2 - data_PvarBW$Dry.Weigh.g.Time1)/data_PvarBW$Dry.Weigh.g.Time1)*100)/data_PvarBW$Days.Time2 #calculate growth rate for time2

# mean, standard dev, and sem
time1_PvarBW <-ddply(data_PvarBW, .( Treatment), summarize, #For each subset of a data frame, apply function then combine results into a data frame.
              N=length(na.omit(time1.growth)), # the sample size of the light column summarized by Tank number
              mean = (mean(time1.growth, na.rm=TRUE)) ,  #take the average of the light column summarized by Tank number
              sd = sd(time1.growth, na.rm=TRUE) ,# the standard deviation of the temp column summarized by Tank number
              sem = (sd(time1.growth,na.rm=T)/sqrt(N))) #calculate the SEM as the sd/sqrt of the count or data length
time1_PvarBW$Time <- "Time1"  # this puts these data in our "time1" dataframe

time2_PvarBW <-ddply(data_PvarBW, .( Treatment), summarize, #For each subset of a data frame, apply function then combine results into a data frame.
              N=length(na.omit(time2.growth)), # the sample size of the light column summarized by Tank number
              mean = (mean(time2.growth, na.rm=TRUE)) ,  #take the average of the light column summarized by Tank number
              sd = sd(time2.growth, na.rm=TRUE) ,# the standard deviation of the temp column summarized by Tank number
              sem = (sd(time2.growth,na.rm=T)/sqrt(N))) #calculate the SEM as the sd/sqrt of the count or data length
time2_PvarBW$Time <- "Time2"  # this puts these data in our "time1" dataframe

#save this dataframe as "G"
G_PvarA <- rbind(time1_PvarBW[1,],time2_PvarBW[1,])# Greate a new column that we rename each row by treatment
G_PvarH <- rbind(time1_PvarBW[2,],time2_PvarBW[2,])# Greate a new column that we rename each row by treatment
G_Pvar<-rbind(G_PvarA, G_PvarH)
# Stress.Recovery column 
 # make new column that renames "time" to Stress or Recovery
G_Pvar$newtime = ifelse(G_Pvar$Time == "Time1", "Post-Stress", "Post-Recovery")
G_Pvar <- within(G_Pvar, newtime <- factor(newtime, levels = c("Post-Stress", "Post-Recovery"))) # Set order of levels so plots in right order



Pvar_BW_plot<-ggplot(data=G_Pvar, aes(x=newtime, y=mean, group = Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Treatment), size=4, show.legend = T)+  
  geom_line(aes(color=Treatment),linetype="dotted")+
  scale_color_manual(values=c("dodgerblue3", "darkred"))+
   geom_point(shape = 1,size = 4,colour = "black")+
  xlab("Time Point") + #Label the X Axis
      ylim(0, .7)+
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border 
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("Dry.Weigh.g"))) +
  ggtitle("Calcification Pvar")+
  theme(plot.title = element_text(size=20, face = "italic", hjust=0.5));Pvar_BW_plot

```
P acuta
```{r}
BWCalc_Pacu <- function(StandardAir= 39.092, Temp, BW, CoralDensity = 1.78){
  #Parameters---------------------------------------------------------------
  # StandardAir is the weight of the Standard in air (Default set at 39.092 grams weighed on balance)
  # Temp is the temperature of the water during the coral measurement
  # BW is the buoywant weight of the coral
  # CoralDensity <- 2.03 #g cm-3, set aragonite density for Montipora from literature 
  # Montipora Arag = 2.03 g cm-3 average from table 2 in Anthony 2003 Functional Ecology 17:246-259
  
  # Porites asteroides (T Hughes 1987 1.69 at 5m) (KB got 1.82)
  
  # below: Medellin-Maldonado et al 2016
  # Pavona varians 1.04 +-0.07
  # panama 8.5380° N, 80.7821° W, 
  # coasta rica 9.7489° N, 83.7534° W
  # mexico la entrega 15.7424° N, 96.1282° W
  # hawaii 19.8968° N, 155.5828° W
  # Pocillopora 1.78 +- 0.31
  
  
  # You can change the density to literatrue values for the specific coral species of interest in the function. 
  
  #Calculation------------------------------------------------------------
  #Step 1: correct the Standard weights for temperature
  # StandardFresh is the weight of the Standard in  fresh water at temp x
  # StandardSalt is the weight of the Standard in salt water at temp x
  
  # This is based on a calibration curve for Standards weighed in fresh and salt water at many temps
  StandardFresh <- StandardFreshModel$coef[-1]*Temp + StandardFreshModel$coef[1] 
  StandardSalt <- StandardSaltModel$coef[-1]*Temp + StandardSaltModel$coef[1] 
  
  # Step 2: Use weight in air and freshwater of the glass Standard to calculate
  # the density of the Standard (Davies eq. 4)
  FreshDensity <- 1 #Fresh water has a density of 1 g/cm3
  StandardDensity <- FreshDensity/(1-(StandardFresh/StandardAir)) 
  
  # Step 3: Calculate the density of seawater using the density of the Standard
  # (Spencer Davies eq. 3)
  SWDensity <- StandardDensity*(1-(StandardSalt/StandardAir))
  
  # Step 4: Calculate the dry weight of the coral (Davies eq. 1)
  CoralWeight <- BW_Pacu/(1-(SWDensity/CoralDensity))
  
  return(CoralWeight) #returns coral dry weights in g
}

Pacu_BW$Dry.Weigh.g <- BWCalc_Pacu(BW=BW_Pacu, Temp=Temp_Pacu) #use function to calculate dry weight
hist(Pacu_BW$Dry.Weigh.g) #not normal
Pacu_BW$Dry.Weigh.g_log<-log10(Pacu_BW$Dry.Weigh.g+1)
hist(Pacu_BW$Dry.Weigh.g_log) #better still tail
boxplot(Pacu_BW$Dry.Weigh.g) #examine data

# below, we are getting rid of columns we don't need anymore, and reorganizing the data by Fragment and clade/color and treatment. This way our time points wil be in the same row)
data_PacuBW <- reshape(Pacu_BW, timevar = "TimePoint", drop = c("Mass.g","Temp.C", "Date","Tank", "X",  "Parent.ID", "Species","Time.Point", "Tank.num"), idvar=c("Frag.ID", "Treatment"), direction="wide")

# This calculates the growth rate, if you look it takes Timepoint1 subtracts timepoint0 and divides by timepoint 0, times 100
data_PacuBW$time1.growth <- (((data_PacuBW$Dry.Weigh.g.Time1 - data_PacuBW$Dry.Weigh.g.Time0)/data_PacuBW$Dry.Weigh.g.Time0)*100)/data_PacuBW$Days.Time1 #calculate growth rate for time1
data_PacuBW$time2.growth <- (((data_PacuBW$Dry.Weigh.g.Time2 - data_PacuBW$Dry.Weigh.g.Time1)/data_PacuBW$Dry.Weigh.g.Time1)*100)/data_PacuBW$Days.Time2 #calculate growth rate for time2



# mean, standard dev, and sem
time1_PacuBW <-ddply(data_PacuBW, .( Treatment), summarize, #For each subset of a data frame, apply function then combine results into a data frame.
              N=length(na.omit(time1.growth)), # the sample size of the light column summarized by Tank number
              mean = (mean(time1.growth, na.rm=TRUE)) ,  #take the average of the light column summarized by Tank number
              sd = sd(time1.growth, na.rm=TRUE) ,# the standard deviation of the temp column summarized by Tank number
              sem = (sd(time1.growth,na.rm=T)/sqrt(N))) #calculate the SEM as the sd/sqrt of the count or data length
time1_PacuBW$Time <- "Time1"  # this puts these data in our "time1" dataframe

time2_PacuBW <-ddply(data_PacuBW, .( Treatment), summarize, #For each subset of a data frame, apply function then combine results into a data frame.
              N=length(na.omit(time2.growth)), # the sample size of the light column summarized by Tank number
              mean = (mean(time2.growth, na.rm=TRUE)) ,  #take the average of the light column summarized by Tank number
              sd = sd(time2.growth, na.rm=TRUE) ,# the standard deviation of the temp column summarized by Tank number
              sem = (sd(time2.growth,na.rm=T)/sqrt(N))) #calculate the SEM as the sd/sqrt of the count or data length
time2_PacuBW$Time <- "Time2"  # this puts these data in our "time1" dataframe

#save this dataframe as "G"
G_PacuA <- rbind(time1_PacuBW[1,],time2_PacuBW[1,])# Greate a new column that we rename each row by treatment
G_PacuH <- rbind(time1_PacuBW[2,],time2_PacuBW[2,])# Greate a new column that we rename each row by treatment
G_Pacu<-rbind(G_PacuA, G_PacuH)
# Stress.Recovery column 
 # make new column that renames "time" to Stress or Recovery
G_Pacu$newtime = ifelse(G_Pacu$Time == "Time1", "Post-Stress", "Post-Recovery")
G_Pacu <- within(G_Pacu, newtime <- factor(newtime, levels = c("Post-Stress", "Post-Recovery"))) # Set order of levels so plots in right order



Pacu_BW_plot<-ggplot(data=G_Pacu, aes(x=newtime, y=mean, group = Treatment, color=Treatment)) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Treatment), size=4, show.legend = T)+  
  geom_line(aes(color=Treatment),linetype="dotted")+
  scale_color_manual(values=c("dodgerblue3", "darkred"))+
   geom_point(shape = 1,size = 4,colour = "black")+
  xlab("Time Point") + #Label the X Axis
      ylim(0, .7)+
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border 
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("Dry.Weigh.g"))) +
  ggtitle("Calcification Pacu")+
  theme(plot.title = element_text(size=20, face = "italic", hjust=0.5));Pacu_BW_plot

```

stats
```{r}
Growth<- rbind(data_McapBW, data_PcompBW, data_PvarBW, data_PacuBW)
GrowthKeep<- c("Frag.ID","time1.growth","time2.growth", "Treatment")
Growth <- Growth[GrowthKeep]

Grow_m <- melt(Growth, id=c("Frag.ID","Treatment")) #melt
names(Grow_m)[names(Grow_m) == "value"] <- "percent.change"
names(Grow_m)[names(Grow_m) == "variable"] <- "Time.point"

Growth2<-merge(Grow_m, meta) #merge metadata
GrowthKeep2<- c("Frag.ID","Time.point", "Treatment", "Tank.num","Parent.ID","Species","percent.change")
Growth3 <- Growth2[GrowthKeep2]
Growth3<-na.omit(Growth3)

hist(Growth3$percent.change) 
Growth3$percent.change_log<-log10(Growth3$percent.change+1)
hist(Growth3$percent.change_log) #normal 

BW_model<-lmer(percent.change_log~Time.point*Treatment*Species+(1|Parent.ID)+(1|Tank.num), Growth3)
anova(BW_model) 
qqPlot(residuals(BW_model)) 

  emm<-emmeans(BW_model,  ~ Time.point*Treatment|Species, adjust="Tukey")
cld(emm)
pairs(emm)

```



#Chl-a
dfs: Slurry=airbrush, SA=wax dip, 
```{r}

 # Plate 1

Chla_plate1<- read.csv("Data/Chla_plate1.csv")

#merge 
ChlaData1 <- merge(meta, Chla_plate1)
ChlaData1 <- merge(ChlaData1, Slurry)
ChlaData1 <- merge(ChlaData1, SA)
ChlaData1$Parent.ID<-as.factor(as.character(ChlaData1$Parent.ID))
ChlaData1$Tank.num<-as.factor(as.character(ChlaData1$Tank.num))
ChlaData1$Surface.area<-as.numeric(as.character(ChlaData1$Surface.area))


ChlaData1$totChla1<-ChlaData1$Rep1*ChlaData1$TotalVolume
ChlaData1$chlaSA1 <- ChlaData1$totChla1/ChlaData1$Surface.area

ChlaData1$totChla2<-ChlaData1$Rep2*ChlaData1$TotalVolume
ChlaData1$chlaSA2 <- ChlaData1$totChla2/ChlaData1$Surface.area

plate1<-plot(ChlaData1$chlaSA1,ChlaData1$chlaSA2)

# Plate 2
Chla_plate2<- read.csv("Data/Chla_plate2.csv")

#merge 
ChlaData2 <- merge(meta, Chla_plate2)
ChlaData2 <- merge(ChlaData2, Slurry)
ChlaData2 <- merge(ChlaData2, SA)
ChlaData2$Parent.ID<-as.factor(as.character(ChlaData2$Parent.ID))
ChlaData2$Tank.num<-as.factor(as.character(ChlaData2$Tank.num))
ChlaData2$Surface.area<-as.numeric(as.character(ChlaData2$Surface.area))

ChlaData2$totChla1<-ChlaData2$Rep1*ChlaData2$TotalVolume
ChlaData2$chlaSA1 <- ChlaData2$totChla1/ChlaData2$Surface.area

ChlaData2$totChla2<-ChlaData2$Rep2*ChlaData2$TotalVolume
ChlaData2$chlaSA2 <- ChlaData2$totChla2/ChlaData2$Surface.area

plate2<-plot(ChlaData2$chlaSA1,ChlaData2$chlaSA2)

# Plate 3
Chla_plate3<- read.csv("Data/Chla_plate3.csv")

#merge 
ChlaData3 <- merge(meta, Chla_plate3)
ChlaData3 <- merge(ChlaData3, Slurry)
ChlaData3 <- merge(ChlaData3, SA)
ChlaData3$Parent.ID<-as.factor(as.character(ChlaData3$Parent.ID))
ChlaData3$Tank.num<-as.factor(as.character(ChlaData3$Tank.num))
ChlaData3$Surface.area<-as.numeric(as.character(ChlaData3$Surface.area))

ChlaData3$totChla1<-ChlaData3$Rep1*ChlaData3$TotalVolume
ChlaData3$chlaSA1 <- ChlaData3$totChla1/ChlaData3$Surface.area

ChlaData3$totChla2<-ChlaData3$Rep2*ChlaData3$TotalVolume
ChlaData3$chlaSA2 <- ChlaData3$totChla2/ChlaData3$Surface.area

plate3<-plot(ChlaData3$chlaSA1,ChlaData3$chlaSA2) #check

# Plate 4 
Chla_plate4<- read.csv("Data/test_plate4.csv")

#merge 
ChlaData4 <- merge(meta, Chla_plate4)
ChlaData4 <- merge(ChlaData4, Slurry)
ChlaData4 <- merge(ChlaData4, SA)
ChlaData4$Parent.ID<-as.factor(as.character(ChlaData4$Parent.ID))
ChlaData4$Tank.num<-as.factor(as.character(ChlaData4$Tank.num))
ChlaData4$Surface.area<-as.numeric(as.character(ChlaData4$Surface.area))


ChlaData4$totChla1<-ChlaData4$Rep1*ChlaData4$TotalVolume
ChlaData4$chlaSA1 <- ChlaData4$totChla1/ChlaData4$Surface.area

ChlaData4$totChla2<-ChlaData4$Rep2*ChlaData4$TotalVolume
ChlaData4$chlaSA2 <- ChlaData4$totChla2/ChlaData4$Surface.area

plate4<-plot(ChlaData4$chlaSA1,ChlaData4$chlaSA2)

# Plate 5 20190319
Chla_plate5<- read.csv("Data/Chla_20190319_plate5.csv")

#merge 
ChlaData5 <- merge(meta, Chla_plate5)
ChlaData5 <- merge(ChlaData5, Slurry)
ChlaData5 <- merge(ChlaData5, SA)
ChlaData5$Parent.ID<-as.factor(as.character(ChlaData5$Parent.ID))
ChlaData5$Tank.num<-as.factor(as.character(ChlaData5$Tank.num))
ChlaData5$Surface.area<-as.numeric(as.character(ChlaData5$Surface.area))


ChlaData5$totChla1<-ChlaData5$Rep1*ChlaData5$TotalVolume
ChlaData5$chlaSA1 <- ChlaData5$totChla1/ChlaData5$Surface.area

ChlaData5$totChla2<-ChlaData5$Rep2*ChlaData5$TotalVolume
ChlaData5$chlaSA2 <- ChlaData5$totChla2/ChlaData5$Surface.area

plate5<-plot(ChlaData5$chlaSA1,ChlaData5$chlaSA2) #some not close, check 

```

means
```{r}
Chla<-rbind(ChlaData1, ChlaData2, ChlaData3, ChlaData4, ChlaData5)



# figure out how to qc this data, how close do numbers need to be and then cut the ones that don't make it. Also make sure no duplicates for frag.ids. THen figure out means. 









# divide by species
Mcap_chla<-subset(Chla, Species =="Montipora_capitata")
Pcomp_chla<-subset(Chla, Species =="Porites_compressa")
Pvar_chla<-subset(Chla, Species =="Pavona_varians")
Pacu_chla<-subset(Chla, Species =="Pocillopora_acuta")

# Mcap
Mcap_chla_Sum <- ddply(Mcap_chla, c("Treatment", "Species", "Time.Point"), summarise, #summarize cell counts
                   N    = length(chla.SA[!is.na(chla.SA)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                   mean = mean(chla.SA, na.rm=TRUE), #calculate mean of response variable, removing NA's
                   sd   = sd(chla.SA, na.rm=TRUE), #calculate standard deviation
                   se   = sd / sqrt(N), #calculate standard error
                   max = max(chla.SA, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
Mcap_chla_Sum #display table

# Pcomp
PcompSum <- ddply(Pcomp, c("Treatment", "Species", "Time.Point"), summarise, #summarize cell counts
                   N    = length(chla.SA[!is.na(chla.SA)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                   mean = mean(chla.SA, na.rm=TRUE), #calculate mean of response variable, removing NA's
                   sd   = sd(chla.SA, na.rm=TRUE), #calculate standard deviation
                   se   = sd / sqrt(N), #calculate standard error
                   max = max(chla.SA, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
PcompSum #display table


# Pvar
PvarSum <- ddply(Pvar, c("Treatment", "Species", "Time.Point"), summarise, #summarize cell counts
                   N    = length(chla.SA[!is.na(chla.SA)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                   mean = mean(chla.SA, na.rm=TRUE), #calculate mean of response variable, removing NA's
                   sd   = sd(chla.SA, na.rm=TRUE), #calculate standard deviation
                   se   = sd / sqrt(N), #calculate standard error
                   max = max(chla.SA, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
PvarSum #display table

# Pacu
PacuSum <- ddply(Pacu, c("Treatment", "Species", "Time.Point"), summarise, #summarize cell counts
                   N    = length(chla.SA[!is.na(chla.SA)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                   mean = mean(chla.SA, na.rm=TRUE), #calculate mean of response variable, removing NA's
                   sd   = sd(chla.SA, na.rm=TRUE), #calculate standard deviation
                   se   = sd / sqrt(N), #calculate standard error
                   max = max(chla.SA, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
PacuSum #display table






```